---
title: "Data Merge"
author: "Samantha Lapehn"
date: "2023-11-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Merge Nov 2023
Performing a merge of CANDLE/GAPPS data with available placenta cell line data as of Nov 2023. 

### Load Packages
```{r packages}
library(tidyverse)
```

### Load Data
Data contains: 
CANDLE/GAPPS placentas
3 primary trophoblast 
5 HTR-8/SVneo
9 BeWo (8 w/unfused, 3 w/fused some with both)
5 JEG-3
4 JAR
2 Explants (one 1st tri, one 2nd tri)
```{r load data}
#Primary Trophoblast
load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/Paquette_Controls_Primary_siRNA_030323.RData")
PrimaryTrophoblast_1 <- Paquette_Primary_siRNA_Controls_Annotated
load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/Paquette_Controls_Primary_DMSO_030323.RData")
PrimaryTrophoblast_2 <- Paquette_Primary_DMSO_Controls_Annotated
load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/Paquette_Controls_PrimaryCRH_071923.RData")
PrimaryTrophoblast_3 <- Paquette_PrimaryCRH_Controls_Annotated

#HTR-8/SVneo
load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/GSE103035_HTR8SVneo_Controls_040323.RData")
HTR8_1<-GSE103035_HTR8SVneo_Controls_Annotated

load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/Paquette_Controls_HTR8SVneo_030323.RData")
HTR8_2 <- Paquette_HTR8_Controls_Annotated

load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/GSE197810_HTR8SVneo_Controls_030723.RData")
HTR8_3 <- GSE197810_HTR8_Controls_Annotated

load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/GSE154339_HTR8SVneo_Controls_033023.RData")
HTR8_4<-GSE154339_Controls_Annotated

load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/GSE85995_Controls_HTR8SVneo_040423.RData")
HTR8_5 <-GSE85995_Controls_Annotated


#BeWo 

load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/GSE66962_Controls_BeWo_030123.RData")
Bewo_1 <- GSE66962_Controls_Annotated

load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/GSE197810_BeWo_Controls_030723.RData")
Bewo_2 <- GSE197810_BeWo_Controls_Annotated

load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/GSE200983_BeWo_Controls_030723.RData")
Bewo_3 <- GSE200983_Controls_Annotated

load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/GSE171648_Controls_BeWo_040623.RData")
Bewo_4 <- GSE171648_Controls_Annotated
Bewo_4$entrezgene_id <-as.numeric(Bewo_4$entrezgene_id)

load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/GSE106394_BeWo_Controls_041923.RData")
Bewo_5 <- GSE106394_BeWo_Controls_Annotated

load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/GSE72437_Controls_BeWo_040723.RData")
Bewo_6 <- GSE72437_BeWo_Controls_Annotated

load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/GSE175815_BeWo_Controls_041123.RData")
Bewo_7 <-GSE175815_BeWo_Controls_Annotated

load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/GSE209620_BeWo_Controls_041923.RData")
Bewo_8 <- GSE209620_BeWo_Controls_Annotated

load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/Paquette_Controls_BeWo_071223.RData")
Bewo_9 <- Paquette_BeWo_Controls_Annotated


#JEG-3
load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/GSE143859_Controls_JEG3_030723.RData")
JEG3_1 <- GSE143859_Controls_Annotated

load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/GSE185071_JEG3_Controls_040423.RData")
JEG3_2 <- GSE185071_JEG3_Controls_Annotated

load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/GSE72437_Controls_JEG3_040723.RData")
JEG3_3 <- GSE72437_JEG3_Controls_Annotated

load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/GSE106394_JEG3_Controls_041923.RData")
JEG3_4 <- GSE106394_JEG3_Controls_Annotated

load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/GSE192446_JEG3_Controls_040323.RData")
JEG3_5 <- GSE192446_JEG3_Controls_Annotated

#JAR
load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/GSE106394_JAR_Controls_041923.RData")
JAR_1 <- GSE106394_JAR_Controls_Annotated

load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/GSE216043_JAR_Controls_040423.RData")
JAR_2 <- GSE216043_JAR_Controls_Annotated

load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/GSE192446_JAR_Controls_040323.RData")
JAR_3 <- GSE192446_JAR_Controls_Annotated

load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/GSE199278_JAR_Controls_040423.RData")
JAR_4 <- GSE199278_JAR_Controls_Annotated

#Explants
load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/GSE154489_Explant_Controls_033023.RData")
Explant_1 <- GSE154489_Controls_Annotated

load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/GSE104348_Controls_Explant_033123.RData")
Explant_2 <- GSE104348_Controls_Annotated

#CANDLE and GAPPS
load(file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Unfiltered Data/CANDLE_GAPPS_Unfiltered_041123.RData")
CANDLE_GAPPS <- candle_gapps_annotated %>%
  dplyr::rename(ensembl_gene_id = ENSEMBL) %>%
  dplyr::rename(hgnc_symbol = SYMBOL) %>%
  dplyr::rename(gene_biotype = BIOTYPE) %>%
  dplyr::rename(description = DESCRIPTION)
```

### Remove unneeded annotation
Only keeping hgnc_symbol, ensembl_gene_id, and gene_biotype
```{r remove unneeded annotation}
PrimaryTrophoblast_1 <- PrimaryTrophoblast_1 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

PrimaryTrophoblast_2 <- PrimaryTrophoblast_2 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

PrimaryTrophoblast_3 <- PrimaryTrophoblast_3 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

HTR8_1 <- HTR8_1 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

HTR8_2 <- HTR8_2 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

HTR8_3 <- HTR8_3 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

HTR8_4 <- HTR8_4 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

HTR8_5 <- HTR8_5 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

Bewo_1 <- Bewo_1 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

Bewo_2 <- Bewo_2 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

Bewo_3 <- Bewo_3 %>%
 dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

Bewo_4 <- Bewo_4 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

Bewo_5 <- Bewo_5 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

Bewo_6 <- Bewo_6 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

Bewo_7 <- Bewo_7 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

Bewo_8 <- Bewo_8 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

Bewo_9 <- Bewo_9 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

JAR_1 <- JAR_1 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

JAR_2 <- JAR_2 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

JAR_3 <- JAR_3 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

JAR_4 <- JAR_4 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

JEG3_1 <- JEG3_1 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

JEG3_2 <- JEG3_2 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

JEG3_3 <- JEG3_3 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

JEG3_4 <- JEG3_4 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

JEG3_5 <- JEG3_5 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

Explant_1 <- Explant_1 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

Explant_2 <- Explant_2 %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -hgnc_id, -entrezgene_id, -chromosome_name, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)

CANDLE_GAPPS <- CANDLE_GAPPS %>%
  dplyr::filter(gene_biotype=="protein_coding") %>%
  dplyr::select(-description, -gene_biotype) %>%
  dplyr::distinct(ensembl_gene_id, .keep_all = TRUE) %>%
  dplyr::distinct(hgnc_symbol, .keep_all=TRUE)
```


### Merge data by CellType
```{r cell type merge}
#Primary Trophoblast
PrimaryTrophoblast_1_2 <- full_join(PrimaryTrophoblast_1, PrimaryTrophoblast_2)
PrimaryTrophoblast_All <- full_join(PrimaryTrophoblast_1_2, PrimaryTrophoblast_3)
#save(PrimaryTrophoblast_All, file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Merged Cell Line Unfiltered Data/PrimaryTrophoblast_Merged_Unfiltered_111723.Rdata")

#HTR-8/SVneo
HTR8_1_2 <- full_join(HTR8_1, HTR8_2)
HTR8_1_2_3 <- full_join(HTR8_1_2, HTR8_3)
HTR8_1_2_3_4 <- full_join(HTR8_1_2_3, HTR8_4)
HTR8_All<- full_join(HTR8_1_2_3_4, HTR8_5)
#save(HTR8_All, file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Merged Cell Line Unfiltered Data/HTR8SVneo_Merged_Unfiltered_111723.Rdata")

#BeWo
Bewo_1_2 <-full_join(Bewo_1, Bewo_2)
Bewo_1_2_3 <- full_join(Bewo_1_2, Bewo_3)
Bewo_1_2_3_4 <- full_join(Bewo_1_2_3, Bewo_4)
Bewo_1_2_3_4_5 <- full_join(Bewo_1_2_3_4, Bewo_5)
Bewo_1_2_3_4_5_6 <- full_join(Bewo_1_2_3_4_5, Bewo_6)
Bewo_1_2_3_4_5_6_7 <- full_join(Bewo_1_2_3_4_5_6, Bewo_7)
Bewo_1_2_3_4_5_6_7_8 <- full_join(Bewo_1_2_3_4_5_6_7, Bewo_8)
Bewo_All <- full_join(Bewo_1_2_3_4_5_6_7_8, Bewo_9)

#save(Bewo_All, file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Merged Cell Line Unfiltered Data/BeWo_Merged_Unfiltered_111723.Rdata")

#JEG3
JEG3_1_2 <- full_join(JEG3_1, JEG3_2)
JEG3_1_2_3 <- full_join(JEG3_1_2, JEG3_3)
JEG3_1_2_3_4 <- full_join(JEG3_1_2_3, JEG3_4)
JEG3_All <-full_join(JEG3_1_2_3_4, JEG3_5)
#save(JEG3_All, file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Merged Cell Line Unfiltered Data/JEG3_Merged_Unfiltered_111723.Rdata")


#JAR
JAR_1_2<- full_join(JAR_1, JAR_2)
JAR_1_2_3 <- full_join(JAR_1_2, JAR_3)
JAR_All <- full_join(JAR_1_2_3, JAR_4)
#save(JAR_All, file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Merged Cell Line Unfiltered Data/JAR_Merged_Unfiltered_111723.Rdata")

#Explants
Explant_All <- full_join(Explant_1, Explant_2)
#save(Explant_All, file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Merged Cell Line Unfiltered Data/Explant_Merged_Unfiltered_111723.Rdata")

```


### Merge all cell types into one
```{r full merge}
Primary_HTR8 <- full_join(PrimaryTrophoblast_All, HTR8_All)
Primary_HTR8_Bewo <- full_join(Primary_HTR8, Bewo_All)
Primary_HTR8_Bewo_JEG3 <- full_join(Primary_HTR8_Bewo, JEG3_All)
Primary_HTR8_Bewo_JEG3_JAR <-full_join(Primary_HTR8_Bewo_JEG3, JAR_All)
Primary_HTR8_Bewo_JEG3_JAR_Explant <- full_join(Primary_HTR8_Bewo_JEG3_JAR, Explant_All)
FullMerge <- full_join(Primary_HTR8_Bewo_JEG3_JAR_Explant, CANDLE_GAPPS)

```

### Clean data names
Need to make sure the Metadata is in the same order as the samples in the FullMerge dataset
```{r clean}
Sample_Metadata <- read.csv("/active/paquette_a/slapehn/Placenta_CellLine_Comparison/SampleID_Key_Aug2023.csv")

FullMerge_NoAnnot <- FullMerge %>%
  dplyr::select(-ensembl_gene_id, -hgnc_symbol)

FullMerge_AnnotationInfo <-FullMerge %>%
  dplyr::select(ensembl_gene_id, hgnc_symbol)

Sample_ID <- Sample_Metadata$Sample_ID

colnames <-colnames(FullMerge_NoAnnot)

match <-match(Sample_ID, colnames)
setdiff(Sample_ID, colnames)
#Reorder column names to match metadata
Reordered_FullMerge_NoAnnot<-FullMerge_NoAnnot[, match]
#check that reordering is accurate and that the order matches
check <- colnames(Reordered_FullMerge_NoAnnot) == Sample_Metadata$Sample_ID
length(colnames(Reordered_FullMerge_NoAnnot))
sum(check)

#Rename with New IDs
colnames(Reordered_FullMerge_NoAnnot) <- Sample_Metadata$NewID
FullMerge_NewIDs <- Reordered_FullMerge_NoAnnot

#Recombine with annotation information
FullMerge_NewIDs_Annotated <- cbind(FullMerge_AnnotationInfo, FullMerge_NewIDs)

```

## Save Merged/Cleaned Data
```{r save}
#save(FullMerge_NewIDs_Annotated, file="/active/paquette_a/slapehn/Placenta_CellLine_Comparison/Data/Merged Unfiltered Data/FullMerge_Unfiltered_111723.Rdata")
```

